I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-22 Paper/Paper_noProof.tex
MIPplanet

It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound. For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed. We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached. 
The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
$\beta \cdot a = x - \alpha (1-a)$, that is 
$(\beta - \alpha) a = x - \alpha$, i.e. 
$$ a = \frac{x - \alpha}{\beta-\alpha}$$

It thus gives an upper bound at 
$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
\hfill $\square$
\end{proof}

@@

The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes (similar to MIPplanet \cite{MIPplanet}),  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.

>>>>

It remains to prove that the 2 upper bound constraints of 1) LP corresponds to the 2) DeepPoly linear upper bound. For that, we study the upper bound function in the linear variable $a \in  [0,1]$, with $x \in [\alpha,\beta]$ fixed. We have $\hat{x}$ in 1) is upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, x - \alpha (1-a)))$, and this bound can be reached. 
The function $min(\beta \cdot a, x - \alpha (1-a))$ reaches its maximum for 
$\beta \cdot a = x - \alpha (1-a)$, that is 
$(\beta - \alpha) a = x - \alpha$, i.e. 
$ a = \frac{x - \alpha}{\beta-\alpha}$.
It thus gives an upper bound at 
$\beta \cdot a = \beta \frac{x - \alpha}{\beta-\alpha}$, which is exactly the upper-bound function used in DeepPoly.
\hfill $\square$
\end{proof}

@@

The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.

### 2024-01-22 Paper/introduction.tex
MIPplanet

\noindent {\bf Comparison with related work:} Here, we will compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA. Compared with the exact encoding of a DNN using MILP \cite{MILP}, our algorithm can be seen as a way to help the MILP tool by telling it to not spend time to branch on ReLU nodes which have low impact on the particular node we are treating, at the cost of a small inaccuracy. If the ReLU nodes to abstract are chosen accurately, the result should be more accurate than early stopping the MILP algorithm using all the nodes.

>>>>

\noindent {\bf Comparison with related work:} we compare with several (but not all) main verification tools for DNNs, to better explain our methodology and how it differs with the existing SOTA. Compared with the exact encoding of a DNN using MILP \cite{MILP}, 
we select a restricted number of ReLU nodes based on compensating strength to scale to larger DNNs while maintaining good accuracy. Further, compared to MIPplanet \cite{MIPplanet} which 
uses a different selection of ReLU nodes, we compute bounds for all neurons iteratively, reducing drastically the number of ReLU nodes represented exactly for a given neuron (ReLU nodes which were considered for neurons in previous layers are not represented exactly for that neuron, while MIPplanet would need to represent all those ReLU nodes exactly), using many fast computations, more efficient than one large computation.
